### 2023-12-11 sections/4-results.tex
fix to Sieve
messing around with csv and latex
fixed issues in csv_to_latex and added table for fashion-mnist

\subsection{Scaling Behavior}

Figures~\ref{fig:results:fashion-mnist-scaling}, ~\ref{fig:results:glove-25-scaling}, and ~\ref{fig:results:sift-scaling} show the scaling behavior of CAKES on augmented versions of the following ann-benchmark datasets: fashion-mnist under Euclidean distance, deep-image under cosine distance, and glove-25 under cosine distance. 
Figure~\ref{fig:results:random-scaling} shows the scaling behavior of CAKES on a completely randomly generated dataset which does not obey any manifold structure. 
The the horizontal axes in each figure denote the multiplier by which we increased the cardinality of the original dataset with synthetic points (see Section \ref{subsec:methods:synthetic-data}). 
The vertical axes denote throughput in queries per second. Both axes are on a logarithmic scale. In this section, we discuss results only for $k = 10$. 
To see results with other values of $k$, refer to {\color{red} ADD SECTION}.

@@

\subsection{Results against Competitors}

@@

% \begin{table*}[!t]
%     % \renewcommand{\arraystretch}{1.15}
%     \caption{Runtime performance (queries per second) of CAKES vs. other methods, $k=10$}
%     \label{table:results:ann-10}
%     \vskip 0.15in
%     \begin{center}
%         \begin{small}
%             \begin{sc}
%                 \begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
%                     \hline
%                     \textbf{Dataset}  & \multicolumn{2}{|c|}{\textbf{faiss-ivf}} & \multicolumn{2}{|c|}{\textbf{bruteforce-blas}} & \multicolumn{2}{|c|}{\textbf{hnsw(faiss)}} & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
%                     \cline{2-9}
%                     &               Recall & QPS      & Recall & QPS    & Recall & QPS    & Recall & QPS \\
%                     \hline
%                     fashion-mnist & 1.000  & 188.03    & 1.000 & 52.91  & 1.000* & 339.74 & 1.000 & 141,800 \\
%                     \hline
%                     gist          & 1.000 & 3.55  & 1.000 & 2.63        & 0.953 & 149.58  & 1.000 & 76,420 \\
%                     \hline
%                     glove-25      & 1.000 & 78.78  & 1.000 & 33.52      & 1.000 & 552.67  & 0.798 & 94,580 \\
%                     \hline
%                     glove-100     & 1.000 & 21.16  & 1.000 & 16.52      & 0.998 & 155.90  & 0.904 & 4,566 \\
%                     \hline
%                     sift          & 1.000 &  24.52 & 1.000 & 16.40      & 1.000 & 275.07  & 1.000 & 357,400 \\
%                     \hline
%                 \end{tabular}
%             \end{sc}
%         \end{small}
%     \end{center}
%     \vskip -0.1in
% \end{table*}

% \begin{table*}[!t]
%     % \renewcommand{\arraystretch}{1.15}
%     \caption{Runtime performance (queries per second) of CAKES vs. other methods, $k=100$. Other methods did not report results for glove-25. Asterisk on recall value indicates that the algorithm had imperfect recall greater than or equal to 0.9995.}
%     \label{table:results:ann-100}
%     \vskip 0.15in
%     \begin{center}
%         \begin{small}
%             \begin{sc}
%                 \begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
%                     \hline
%                     \textbf{Dataset}  & \multicolumn{2}{|c|}{\textbf{faiss-ivf}} & \multicolumn{2}{|c|}{\textbf{bruteforce-blas}} & \multicolumn{2}{|c|}{\textbf{hnsw(faiss)}} & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
%                     &                    Recall & QPS  & Recall & QPS     & Recall & QPS      & Recall & QPS \\
%                     \hline
%                     fashion-mnist  & 1.000 & 111.47    & 1.000* & 16.02   & 1.000* & 277.80   & 1.000 & 71,370 \\ 
%                     \hline
%                     gist           & 1.000 & 2.70      & 1.000* & 0.80    & 0.995 & 59.71     & 1.000 & 29,090 \\
%                     \hline
%                     glove-25       & -- & --           & --     & --      & -- & --           & 0.851 & 49,350 \\
%                     \hline
%                     glove-100      & 1.000* &  19.04   & 1.000* & 7.52    & 0.987 & 92.58     & 0.905 & 4,384 \\
%                     \hline
%                     sift           & 1.000 &  23.50    & 1.000  & 6.51    & 1.000* & 179.14   & 1.000 & 147,400 \\                                                 
%                     \hline
%                 \end{tabular}
%             \end{sc}
%         \end{small}
%     \end{center}
%     \vskip -0.1in
% \end{table*}

>>>>

Figures~\ref{fig:results:fashion-mnist-scaling}, ~\ref{fig:results:glove-25-scaling}, and ~\ref{fig:results:sift-scaling} show the scaling behavior of CAKES on augmented versions of the following ann-benchmark datasets: fashion-mnist under Euclidean distance, deep-image under cosine distance, and glove-25 under cosine distance. 
Figure~\ref{fig:results:random-scaling} shows the scaling behavior of CAKES on a completely randomly generated dataset which does not obey any manifold structure. 
The the horizontal axes in each figure denote the multiplier by which we increased the cardinality of the original dataset with synthetic points (see Section \ref{subsec:methods:synthetic-data}). 
The vertical axes denote throughput in queries per second. Both axes are on a logarithmic scale. In this section, we discuss results only for $k = 10$. 
To see results with other values of $k$, refer to our Supplement section.

@@

@@

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall of CAKES vs. other methods on the sift dataset. We use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.}
    \label{table:results:ann-fashion}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
                    \hline
                    \textbf{Scaling Factor}  & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf-flat}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall       \\
                    \hline
                    1.000 & 2191.849 & 0.950 & 212.602 & 1.000 & 2009.483 & 1.000 & 2167.365 & 1.000 \\
                    \hline
                    2.000 & 2118.513 & 0.927 & 106.372 & 1.000 & 939.169 & 1.000* & 1141.225 & 1.000 \\
                    \hline
                    4.000 & 2043.628 & 0.898 & 53.077 & 1.000 & 461.016 & 0.997 & 982.117 & 1.000 \\
                    \hline
                    8.000 & 1925.593 & 0.857 & 26.577 & 1.000 & 225.827 & 0.995 & 1179.813 & 1.000 \\
                    \hline
                    16.000 & 1841.863 & 0.862 & 13.292 & 1.000 & 116.960 & 0.991 & 1201.409 & 1.000 \\
                    \hline
                    32.000 & 1850.943 & 0.775 & 6.647 & 1.000 & 59.148 & 0.985 & 1157.667 & 1.000 \\
                    \hline
                    64.000 & 1787.142 & 0.677 & 3.324 & 1.000 & 26.068 & 0.968 & 1102.849 & 1.000 \\
                    \hline
                    128.000 & 1659.660 & 0.538 & 1.662 & 1.000 & 13.265 & 0.964 & 1039.607 & 1.000 \\
                    \hline
                    256.000 & 1597.264 & 0.592 & 0.831 & 1.000 & 6.650 & 0.962 & 1058.972 & 1.000 \\
                    \hline
                    512.000 & 1826.362 & 0.581 & 0.416 & 1.000 & 3.563 & 0.949 & 1035.260 & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}

\begin{table*}[!t]
    % \renewcommand{\arraystretch}{1.15}
    \caption{Runtime performance (queries per second) and recall of CAKES vs. other methods on the fashion-mnist dataset. We use 1.000* to denote that the recall is imperfect, but rounds to 1.000 when we consider only three decimal places.}
    \label{table:results:ann-fashion}
    \vskip 0.15in
    \begin{center}
        \begin{small}
            \begin{sc}
                \begin{tabular}{|l|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
                    \hline
                    \textbf{Scaling Factor}  & \multicolumn{2}{|c|}{\textbf{annoy}} & \multicolumn{2}{|c|}{\textbf{faiss-flat}} & \multicolumn{2}{|c|}{\textbf{faiss-ivf-flat}}  & \multicolumn{2}{|c|}{\textbf{CAKES}} \\
                    \hline
                    &             QPS & Recall        & QPS & Recall      & QPS & Recall       & QPS & Recall       \\
                    \hline
                    1.000 & 2191.849 & 0.950 & 212.602 & 1.000 & 2009.483 & 1.000 & 2167.365 & 1.000 \\
                    \hline
                    2.000 & 2118.513 & 0.927 & 106.372 & 1.000 & 939.169 & 1.000* & 1141.225 & 1.000 \\
                    \hline
                    4.000 & 2043.628 & 0.898 & 53.077 & 1.000 & 461.016 & 0.997 & 982.117 & 1.000 \\
                    \hline
                    8.000 & 1925.593 & 0.857 & 26.577 & 1.000 & 225.827 & 0.995 & 1179.813 & 1.000 \\
                    \hline
                    16.000 & 1841.863 & 0.862 & 13.292 & 1.000 & 116.960 & 0.991 & 1201.409 & 1.000 \\
                    \hline
                    32.000 & 1850.943 & 0.775 & 6.647 & 1.000 & 59.148 & 0.985 & 1157.667 & 1.000 \\
                    \hline
                    64.000 & 1787.142 & 0.677 & 3.324 & 1.000 & 26.068 & 0.968 & 1102.849 & 1.000 \\
                    \hline
                    128.000 & 1659.660 & 0.538 & 1.662 & 1.000 & 13.265 & 0.964 & 1039.607 & 1.000 \\
                    \hline
                    256.000 & 1597.264 & 0.592 & 0.831 & 1.000 & 6.650 & 0.962 & 1058.972 & 1.000 \\
                    \hline
                    512.000 & 1826.362 & 0.581 & 0.416 & 1.000 & 3.563 & 0.949 & 1035.260 & 1.000 \\
                    \hline
                \end{tabular}
            \end{sc}
        \end{small}
    \end{center}
    \vskip -0.1in
\end{table*}
